### 2019-02-19 sections/introduction.tex
scope

\fixme{Rewrite}

In this paper, we set out to develop a formal basis for \TOP, called \TOPHAT (TopHat).
Our goal is to specify the basic building blocks of declarative workflows.
We clearly separate them from general purpose programming concepts.
This allows us to prove properties like progress and type preservation.
\TOPHAT should be powerful enough to model complicated real-world situations,
without losing opportunities for formal reasoning.

By separating them in the style of a deep embedding \cite{conf/cefp/Gibbons13}, we make explicit where and where not, they depend on each other. \fixme{what to do with this sentence}

We show that, where process algebras focus on the \emph{coordination} of processes and the \emph{communication} between them,
\TOP, and therefore \TOPHAT, focus on supporting \emph{tasks} and model ways to \emph{collaborate} on them.

In this paper we aim to identify the essence of \TOP in formal as well as an informal way.
These core principles lead to a formal system for \TOP, called \TOPHAT,
which paves the way to formal reasoning.
Applications written using the \TOP paradigm, like those in \ITASKS and \MTASKS, currently lack such a feature.

\TOP applications give rise to concepts like concurrency, synchronisation, \GUI-programming and program generation.
In this paper we identify common concepts from already existing languages and frameworks,
and describe their similarities and differences.\fixme{What do you mean with this sentence?}

\fixme{Change or remove.}
In this paper we study the essence of \TOP.
We claim that at the heart of \TOP lie modular interactive workflows.
Workflows because \TOP programs coordinate collaboration between people.
Interactive because progress of \TOP programs is driven by user input.
Modular because the embedding in a strongly-typed functional language allows powerful abstractions using type-driven techniques and higher-order functions.

>>>>

In this paper, we set out to develop a formal basis for \TOP, called \TOPHAT (TopHat).
Our goal is to pave the way for formal treatment of \TOP programs.

\ITASKS is the de-facto reference implementation of \TOP.
It has been designed for developing real-world applications, and is constantly being extended and improved with this goal in mind.
All the bells and whistles of \ITASKS, the different variations of task combinators, and the details that come with real-world requirements, make it hard to see what the essence of \TOP is.
It also makes formal reasoning about \TOP programs impossible.

In this paper, we want to take a step back and look at the essence of \TOP.
We do this both formally and informally.
Informally in the sense that we give an intuitive description of the features that define task-oriented programming.
Formally in the sense that we develop a calculus which formalizes these features as language constructs, and we give them semantics in the style that is common in programming language research.

One of the defining aspects of \ITASKS is its embedding in a functional programming language.
This creates a synergy where \ITASKS profits from the expressivity of Clean, while enhancing the language with functionality for user interaction.
The tight integration of task DSL and host language makes it sometimes difficult to see where the boundaries are.

In \TOPHAT, we separate the task layer and the underlying host language, both syntactically and semantically.
In this way we make explicit which of the synergetic effects of \TOP come from the task layer, and which come from functional programming.
